Cryptanalysis of SBC based post-quantum signature scheme

### 2025-06-27 rapport.tex
cGGM construction

		One challenge in this approach is the need to communicate the offset to the verifier so that they can verify the computations. However, a recent technique called \emph{Correlated GGM} (cGGM) has been introduced in \cite{GYWZ+22}, which allows the prover to generate random values $x^{\lir}$ using a modified GGM tree, such that $\sum_{i=1}^{N} x^{\lir} = x$, with minimal computational overhead.

>>>>

		One challenge in this approach is the need to communicate the offset to the verifier so that they can verify the computations. However, a recent technique called \emph{Correlated GGM} (cGGM) has been introduced in \cite{GYWZ+22}, which allows the prover to generate random values $x^{\lir}$ using a modified GGM tree, such that $\sum_{i=1}^{N} x^{\lir} = x$, with no computational.
		This is achieved by enforcing an invariant over the cGGM tree: at each level, the sum of the nodes remains constant. More precisely, given a parent node $x$, the left child is defined as $H(x)$ and the right child as $x - H(x)$, where $H$ is a cryptographic hash function. As a result, only approximately half of the tree nodes require hash evaluations, compared to all nodes in the classical GGM construction.
		This technique not only reduces the computational cost but also eliminates the need to transmit the offset to the verifier, thereby improving the overall communication efficiency.
